CorReg: model-based pretreatment for regression with correlated variables. Application in steel industry

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@488 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{figure}[h!]
	\begin{minipage}[l]{.32\linewidth}
			\includegraphics[width=170px]{figures/MQEn15sigmaY10.png} 
			\caption{For $n=15$. Dotted: \textsc{Correg}, plain: OLS}\label{MQE1}
	\end{minipage} \hfill
	\begin{minipage}[c]{.32\linewidth}
			\includegraphics[ width=170px]{figures/MQEn100sigmaY10.png} 
			\caption{For $n=100$. Dotted: \textsc{Correg}, plain: OLS}
	\end{minipage} \hfill
   \begin{minipage}[r]{.32\linewidth}
			\includegraphics[width=170px]{figures/MQEn1000sigmaY10.png} 
			\caption{For $n=1000$. Dotted: \textsc{Correg}, plain: OLS.} \label{MQE3}
   \end{minipage} 
\end{figure} 
It is clear in Figures \ref{MQE1} to \ref{MQE3} that the reduced model is more robust than OLS. And even when sub-regression are week (small value of $1-\mathcal{R}^2$) it does not explode. We also see that the error implied by strong correlations shrinks whit the rise of $n$.  $MSE_{OLS}=0+\operatorname{Tr}(\operatorname{Var}(\hat{\beta}))=\operatorname{Tr}(\operatorname{Var}(\hat{\beta}_{1}))+\operatorname{Tr}(\operatorname{Var}(\hat{\beta}_{2}))$. both terms are multiplied by $\sigma_Y^2$ and so is $\operatorname{Tr}(\operatorname{Var}(\hat{\alpha}_{1}))$. Thus, as $\operatorname{Var}(\hat{\alpha}_{2})=0$ when $\sigma_Y^2$ rises it increases the advantage of \textsc{CorReg} versus \textsc{OLS}. It illustrates the importance of dimension reduction when the model has a strong noise (very usual case on real datasets where true model is not even exactly linear).

>>>>

\begin{figure}[h!]
	\begin{minipage}[l]{.32\linewidth}
			\includegraphics[width=170px]{figures/MQEn15sigmaY10.png} 
			\caption{For $n=15$. Dotted: \textsc{Correg}, plain: OLS}\label{MQE1}
	\end{minipage} \hfill
	\begin{minipage}[c]{.32\linewidth}
			\includegraphics[ width=170px]{figures/MQEn100sigmaY10.png} 
			\caption{For $n=100$. Dotted: \textsc{Correg}, plain: OLS}
	\end{minipage} \hfill
   \begin{minipage}[r]{.32\linewidth}
			\includegraphics[width=170px]{figures/MQEn1000sigmaY10.png} 
			\caption{For $n=1000$. Dotted: \textsc{Correg}, plain: OLS.} \label{MQE3}
   \end{minipage} 
\end{figure} 
It is clear in Figures \ref{MQE1} to \ref{MQE3} that the marginal model is more robust than \textsc{OLS} on $X$. And when sub-regression get weaker ($1-\mathcal{R}^2$ tends to 1) it does not explode until extreme values (sub-regression nearly fully explained by the noise). We also see that the error implied by strong correlations shrinks whith the rise of $n$.  $MSE_{OLS}=0+\operatorname{Tr}(\operatorname{Var}(\hat{\beta}))=\operatorname{Tr}(\operatorname{Var}(\hat{\beta}_{1}))+\operatorname{Tr}(\operatorname{Var}(\hat{\beta}_{2}))$ where both terms are multiplied by $\sigma_Y^2$ and so is $\operatorname{Tr}(\operatorname{Var}(\hat{\alpha}_{1}))$. Thus, as $\operatorname{Var}(\hat{\alpha}_{2})=0$ when $\sigma_Y^2$ rises it increases the advantage of \textsc{CorReg} versus \textsc{OLS}. It illustrates the importance of dimension reduction when the model has a strong noise (very usual case on real datasets where true model is not even exactly linear).
